% Ronuk Raval's Resume
% Modified from http://www.mcnabbs.org/andrew/linux/latexres/mcnabb-res.tex

\documentclass[11pt,oneside]{article}
\usepackage{geometry}
\usepackage[T1]{fontenc}
\usepackage{hyperref}

\pagestyle{empty}
\geometry{letterpaper,tmargin=1in,bmargin=1in,lmargin=0.75in,rmargin=0.75in,
    headheight=0in,headsep=0in,footskip=.3in}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

% Name and contact information
\newcommand{\name}{Ronuk Raval}
\newcommand{\permaddr}{5999 Cherrywood Pl, Mississauga, ON, L5M 4Z6}
\newcommand{\tempaddr}{
    Room 214,
    Minota Hagey Residence,
    200 University Avenue West,
    Waterloo, ON, N2L 3G1
}
\newcommand{\phone}{(519) 722-3062}
\newcommand{\email}{ronuk.raval@gmail.com}
\newcommand{\website}{http://zeroindexed.com}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% New commands and environments

% This defines how the name looks
\newcommand{\bigname}[1]{
    \begin{center}\fontfamily{phv}\selectfont\Huge\scshape#1\end{center}
}

\newcommand{\respara}[1]{
    \vspace{4pt}
    {\fontfamily{phv} \selectfont \Large #1} \\
    \vspace{4pt}
    \hspace{19pt}
}

% A ressection is a main section (<H1>Section</H1>)
\newenvironment{ressection}[1]{
    \respara{#1}
    \begin{itemize}
    \vspace{-20pt}
}{
    \end{itemize}
}

% A resitem is a simple list element in a ressection (first level)
\newcommand{\resitem}[1]{
    \vspace{-4pt}
    \item \begin{flushleft} #1 \end{flushleft}
}

\newcommand{\resrightitem}[1]{
    \vspace{-4pt}
    \item \begin{flushright} #1 \end{flushright}
}

% A ressubitem is a simple list element in anything but a ressection (second level)
\newcommand{\ressubitem}[1]{
    \vspace{-1pt}
    \item \begin{flushleft} #1 \end{flushleft}
}

% A resbigitem is a complex list element for stuff like jobs and education:
%  Arg 1: Name of company or university
%  Arg 2: Location
%  Arg 3: Title and/or date range
\newcommand{\resbigitem}[3]{
    %\vspace{-5pt}
    \item
    \textbf{#1} \hfill \textit{#2} \\
    #3
}

\newcommand{\eduitem}[4]{
  \item
    \textbf{#1} \hfill \textit{#2} \\ \mbox{} \hfill \textit{#3} \\
    #4
}

% This is a list that comes with a resbigitem
\newenvironment{ressubsec}[3]{
    \resbigitem{#1}{#2}{#3}
    \vspace{-2pt}
    \begin{itemize}
    \vspace{-1.7em}
}{
    \end{itemize}
}

% This is a simple sublist
\newenvironment{reslist}[1]{
    \resitem{\textbf{#1}}
    \vspace{-5pt}
    \begin{itemize}
}{
    \end{itemize}
}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Now for the actual document:

\begin{document}

\fontfamily{ppl} \selectfont

% Name with horizontal rule
\bigname{\name}

\vspace{-8pt} \rule{\textwidth}{1pt}

\vspace{-1pt} {\small\itshape Permanent: \permaddr \hfill \phone; \href{mailto:\email}{\email}\\
    Temporary: \tempaddr}% \hfill Website: \href{\website}{\website}}

\vspace{8 pt}


%%%%%%%%%%%%%%%%%%%%%%%%

\begin{ressection}{Skills}

    \resitem{Proficient with C, C++, Python, Shell scripting, Haskell,
        Javascript, Scheme, and Java; as well as several documentation and testing
        suites respective to those languages.}

    \resitem{Familiar with general database concepts and the SQL-92 standard, as well
        as the MySQL and Oracle implementations.}

    \resitem{Skilled with Linux, Bash and zsh shells, and the UNIX toolchain.}

    \resitem{Working knowledge of several build systems and development environments,
        including handwritten makefiles, the autotools suite, as well as Eclipse,
        Qt Creator, KDevelop, and Eric4.}

    \resitem{Well versed in the use of several revision control systems from the command
        line, namely Subversion, Git, Bazaar, and Darcs, with passing familiarity with
        RCS and CVS.}

    \resitem{Knowledgable about computer hardware and logic level design and abstraction.}

\end{ressection}

\begin{ressection}{Work Experience}

    \begin{ressubsec}{Bloomberg LP: Financial Software Developer}{New York, NY (September -- December, 2010)}

        \ressubitem{Internship as part of the Management Information Systems team.}

        \ressubitem{Designed, tested, and programmed both frontend and backend systems for a search
            feature to be used in a multi-user, highly concurrent manner, featuring both synchronous
            and asynchronous modes of operation. This replaced a legacy system and involved writing
            data migration scripts from an Oracle backend to an in-house proprietary database.}

        \ressubitem{Replaced a few legacy screens written in a mixture of Fortran and C with variants
            that used the newer client-server oriented architecture in C++ and Javascript. Also added
            features and functionality not present in the older screens.}

        \ressubitem{Responsible for writing scripts to migrate the team source code repository system
            from RCS to Subversion. Also wrote scripts that wrapped around Subversion to aid in the
            specific workflow used by the team.}

    \end{ressubsec}

    \resbigitem{University of Waterloo: Campus Recreation}{Waterloo, ON (October -- December, 2009)}
        {Intramural Flag Football Referee.}

    \begin{ressubsec}{St. Joseph Secondary School: Peer As Teacher Helper}{Mississauga, ON (February -- June, 2009)}

        \ressubitem{Teaching assistant for a grade 10 computer engineering class,
            taken as a non-paid co-operative education credit in secondary school.}

        \ressubitem{Given free reign over many activities, including teaching an entire unit
            on Lego Mindstorms robots, marking of assignments, and leading classes where
            the teacher was not present.}

        \ressubitem{Designed, executed, and marked the culminating assignment worth 10\% of
            the students' final grade: to build a servomotor control circuit using two
            555 astable timers and a variable resistor to control the desired angle of the
            servomotor.}

    \end{ressubsec}

    \resbigitem{St. Dunstan Elementary School}{Mississauga, ON (May 2008)}
        {Volunteer Flag Football Coach.}

\end{ressection}

\pagebreak

\begin{ressection}{Open Source Activities}
    \item[] \hspace{-2.6em} Links to respective source repositories can be found at the bottom of this page.

    \resitem{\href{https://github.com/rraval/wlcc}{Currently implementing an optimizing compiler in
        Haskell}~\texttt{[wlcc]}.}

    \resitem{\href{http://zeroindexed.com/cpp-conway}{Wrote a proof of concept Conway's Game of Life
        simulator entirely in the C preprocessor}~\texttt{[cpp-conway]}.}

    \resitem{\href{https://github.com/rraval/Rescue}{Designed a r\'{e}sum\'{e} formatting domain
        specific language implemented in Haskell.}~\texttt{[rescue]}.}

    \resitem{\href{http://gitorious.org/jockey}{Partially completed a note storing system in
        Python}~\texttt{[jockey]}.}

    \resitem{\href{http://launchpad.net/wicd}{Contributed a command line interface to the wicd
        network manager for Linux}~\texttt{[wicd]}.}

    \resitem{\href{http://code.launchpad.net/~ronuk-raval/+junk/xtest}{Wrote a Python interface
        to the XTest extension of the X server}~\texttt{[xtest]}.}

\end{ressection}

\begin{ressection}{Education}

    \resbigitem{University of Waterloo}{Waterloo, ON (September 2009 -- present)}
        {Candidate for Bachelor of Computer Science\\Honours Computer Science
            with Digital Hardware Option, Co-op Program}

    \begin{reslist}{Relevant Courses and Assignments}

        \resbigitem{Foundations of Sequential Programs}{University of Waterloo (January -- April, 2010)}
            {Completed an optimizing toolchain that compiled a C derived
            language (named \textit{WL}) to a subset of the MIPS instruction set,
            going far beyond course expectations.}

        \resbigitem{Design, Abstraction, and Implementation}{University of Waterloo (September -- December, 2009)}
            {Accepted in an instructor consent only advanced level first year
            computer science course, with a focus on data structures, formalism,
            and models.}

        \resbigitem{Computer and Information Science}{St. Joseph Secondary School (February -- June, 2009)}
            {Partially finished a substitute teacher allocation
            application as a special project assigned by the secondary school.}

    \end{reslist}

\end{ressection}


%\begin{ressection}{Clubs}
%
%  \resitem{\textbf{Judo:} Practicing Member. \hfill
%    \textit{University of Waterloo (January 2010 -- present)}}
%
%  \begin{ressubsec}{Robotics}{St Joseph Secondary School (September 2007 -- June 2009)}
%
%    \ressubitem{Team lead from September 2008 to June 2009.}
%
%    \ressubitem{Wrote driver code for an intelligent sumo robot in a low level C derived language
%      for the Lego Mindstorms NXT processor.}
%
%    \ressubitem{Designed and built two robots for the Canadian Skills Competition in 2008 and 2009.}
%
%  \end{ressubsec}
%
%  \resitem{\textbf{Football:} Team member. \hfill
%    \textit{St. Joseph Secondary School (September -- December, 2006 -- 2009)}}
%
%\end{ressection}

\begin{ressection}{Awards and Achievements}

    \resitem{\textbf{Evaluated "Outstanding"}, the highest possible rating, for
        internship at Bloomberg LP (\textit{2010}).}

    \resitem{\textbf{Most Valued Member:} St. Joseph Robotics Team
        (\textit{2009}).}

    \resitem{\textbf{Best Engineered Robot:} University of Ontario Institute of Technology Lego
      Mindstorms SumoBot competition (\textit{2008}).}

    \resitem{\textbf{Subject Award:} Highest mark in Computer Science that year
        at St. Joseph Secondary School (\textit{2007}).}

    \resitem{\textbf{Most Dedicated Player:} St. Joseph Junior Boys Football
        team (\textit{2007}).}

\end{ressection}

\vfill

\rule{\textwidth}{1pt}
\begin{tabbing}
  \texttt{[wlcc]:\ \ \ \ \ \ \ \ https://github.com/rraval/wlcc}\\
  \texttt{[cpp-conway]: http://zeroindexed.com/cpp-conway}\\
  \texttt{[rescue]:\ \ \ \ \ \ https://github.com/rraval/Rescue}\\
  \texttt{[jockey]:\ \ \ \ \ \ http://gitorious.org/jockey}\\
  \texttt{[wicd]:\ \ \ \ \ \ \ \ http://launchpad.net/wicd}\\
  \texttt{[xtest]:\ \ \ \ \ \ \ http://code.launchpad.net/{\raise.17ex\hbox{$\scriptstyle\mathtt{\sim}$}}ronuk-raval/+junk/xtest}
\end{tabbing}

\end{document}
